\documentclass[12pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{lmodern}
\usepackage{hyperref}

\address{Faculty of Forestry \& Environmental Stewardship\\University of British Columbia\\Vancouver, BC, Canada}
\date{\today}

\begin{document}

\begin{letter}{Editors-in-Chief\\Sustainable Futures}

\opening{Dear Editors-in-Chief,}

We are pleased to submit our manuscript entitled \textit{``Developing a prototype decision support framework to assess forest management scenarios as a nature-based decarbonization solution for the mining sector: A case study in British Columbia, Canada''} for consideration for publication in \textit{Sustainable Futures}.

This study addresses the challenge of decarbonization in hard-to-abate industries by evaluating forest management nature-based solutions (NbS) around mining sites. Our primary contribution is an open-source prototype decision support framework that integrates a forest estate optimizer with carbon accounting (ws3 + libCBM) to explore forest management scenarios. We demonstrate the framework's adaptability across three distinct sites in British Columbia and report environmental indicators and economic trade-offs across objectives (maximize volume, minimize area, maximize carbon stocks, minimize net emissions).

We confirm the manuscript has not been published previously and is not under consideration elsewhere. All authors have approved the final version. The submission package includes the manuscript, highlights, and a graphical abstract (uploaded as a separate file). Data and code are openly available via Zenodo (DOI: 10.5281/zenodo.17316315) and the current project repository at \url{https://github.com/UBC-FRESH/nbds_dss}. Declarations (Funding, CRediT, Competing interest, Data availability) are included in the manuscript, and a declarations tool docx is provided.

Use of AI and AI-assisted technologies: we used a generative AI tool to assist with grammar, consistency, and compliance checks against the journal's author guidelines. No analysis, results, or novel content were generated by AI. The authors take full responsibility for the content of the manuscript.

Thank you for considering our manuscript. We look forward to your response.

Sincerely,

\vspace{1em}
\noindent
Gregory Paradis\\
Assistant Professor\\
Department of Forest Resources Management\\
Faculty of Forestry \& Environmental Stewardship\\
University of British Columbia\\
gregory.paradis@ubc.ca

\end{letter}

\end{document}
