\documentclass[12pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{lmodern}

\address{Faculty of Forestry\\University of British Columbia\\Vancouver, BC, Canada}
\date{October 13, 2025}

\begin{document}

\begin{letter}{Editors-in-Chief\\Cleaner Environmental Systems}

\opening{Dear Editors-in-Chief,}

We are pleased to submit our manuscript entitled \textit{“Developing a prototype decision support framework to assess forest management scenarios as a nature-based decarbonization solution: A case study in British Columbia, Canada”} for consideration for publication in \textit{Cleaner Environmental Systems}.

While the mining sector is under pressure to meet net‑zero emissions by 2050, it may fall short due to technological and financial barriers. Nature‑based solutions (NbS) can complement engineering decarbonization strategies. Our primary contribution is an open‑source, prototype decision support framework that integrates a forest estate optimizer with carbon accounting (ws3 + libCBM) to explore forest management scenarios as an NbS pathway. We demonstrate the framework’s adaptability across three distinct sites in British Columbia and report environmental (carbon stocks and net emissions), economic (revenue), and social (jobs) indicators to illustrate trade‑offs among objectives (max volume, min area, max carbon, min net).

We believe the manuscript aligns with the objectives and scope of \textit{Cleaner Environmental Systems} and will be of interest to readers working at the intersection of sustainable industrial practices, land‑use planning, and climate mitigation.

We confirm the manuscript has not been published previously and is not under consideration elsewhere. All authors have approved the final version. The submission package includes: manuscript, title page, highlights, and a graphical abstract (uploaded as a separate figure). Data and code are openly available: archived citation in the manuscript and the current prototype repo at \url{https://github.com/UBC-FRESH/nbds_dss}. Declarations (Funding, CRediT, Competing interest, Data availability) are included in the manuscript.

Use of AI and AI‑assisted technologies: in the final stage of editing and packaging, we used a generative AI tool to help check compliance with the CES Guide for Authors (e.g., highlights length/format, declarations present) and to improve grammar and consistency. No analysis, results, or novel content were generated by AI. The authors take full responsibility for the content of the manuscript.

Thank you for considering our manuscript. We look forward to your response.

Sincerely,

\vspace{1em}
\noindent
Gregory Paradis\\
Assistant Professor\\
Department of Forest Resources Management\\
Faculty of Forestry\\
University of British Columbia\\
gregory.paradis@ubc.ca

\end{letter}

\end{document}

